Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
started pass over mcmc

\subsection{Whitened Histograms of Orientations (WHO)}

Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables
\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,
\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
\end{equation}
, we remove 2nd order correlation between all features. Since covarinace
collection is expensive, \cite{Hariharan12} proposed easy way to generate
covariance $\Sigma$ from autocovariance $\Gamma$

@@

\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
Our first innovation is `Non-Zero' whitening. When synthesizing detection
templates from rendered images, a common problem is how to handle the
background. If the model is rendered over a natural image background, gradients
in the background will be incorporated into the discriminative template,
potentially causing false-positives if background elements exist in the query
image.

@@

\section{Estimating Parameters using MCMC}
\label{sec:fine}
% Estimating viewpoint continuously to fine tune a initial matching
The NZ-WHO template matching method we have presented makes template generation
and evaluation computationally inexpensive. This means we can efficiently
explore the parameter space to find the best object pose, scale, model type and
camera focal length.

Since creating a template and validating the template become computationally
inexpensive, making a proposal and validating the proposal to fine tune a 2D-3D
matching became affordable. We used Metropolis-Hastings algorithm to generate a
proposal pose and focal length and validate the proposal using the convolution
and returning maximum response as a return.

To fine-tune continuous pose and location of object, we require strong
initialization. The initialization is a rough bounding box with small context
and viewpoint. Since most of the standard detectors does not provide viewpoint
of an object, we first run an ensemble of NZ-WHO templates to get rough
viewpoints. Once we get rough viewpoint, we initialize the proposal $x_0$ and
start sampling proposals.

We modeled the distribution of object location and pose as an exponential distribution. 
For proposal distribution, we used Gaussian distribution to propose next viewpoint and for viewpoint proposals
and uniform distribution for model change proposals.

More formally, suppose that $x = [p, m, f]$ where $p$ is the 3D rotation of the CAD model and
$m$ is the CAD model index and $f$ is the focal length. We use Metropolis Hastings
to optimize $x$.

\begin{align}
    A(x \rightarrow x') & =  min\left( 1,  \frac{P(x' g(x') \rightarrow x)}{P(x) g(x \rightarrow x')}\right) \\
    g(x \rightarrow x + p_i') & \sim \mathcal{N}(\mu = 0,\sigma = c_1) \quad i \in \{1,2,3\}\\
    g(x \rightarrow x + f') & \sim \mathcal{N}(\mu = 0,\sigma = c_2)\\
    g(x \rightarrow x + m') & \sim c_3 \delta(m) + (1-c_3) Unif(1,M)
\end{align}

Where $g$ is the proposal distribution and $P$ is the distribution of which we
defined using Gaussian distribution around previous state. $A$ is the
acceptance probability where we accept new proposal with $A(x \rightarrow x')$.

\begin{align}
    P(x) & \sim e^{ c_4 \max_{s} w(x) \ast \mathcal{T}_s(\mathcal{I}) }
\end{align}

$P$ is the distribution of the pose and location of an object on image
$\mathcal{I}$. One can also think of the image as an image cropped by detection
bounding box. We synthesize covariance matrix and create NZ-WHO template $w(x)$ for particular viewpoint, focal length and CAD model.

We initialize the $x$ using the result from the previous stage where we run our ensemble or NZ-WHO templates to get rough estimate.

In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
We found out that it requires good initialization to converge to local minima.

We represented the probability using exponential family.

So our model favors large convolution score $\max_{s} w(x) \ast T(\mathcal{I})$. 
% there are several advantages that was not possible such as \textbf{on-the-fly} template generation and making large number of templates  
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Different modes of Metropolis Hasting proposals, see Section \ref{sec:fine}}
 \label{fig:tuningmode}
\end{figure}

\section{Experiments}
\label{sec:experiments}
\input{experiments}

>>>>

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Recently, Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables
\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,
\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
\end{equation}
, we remove 2nd order correlation between all features. Since covarinace
collection is expensive, \cite{Hariharan12} proposed easy way to generate
covariance $\Sigma$ from autocovariance $\Gamma$

@@

\subsubsection{Whitening Synthesized Templates and Non-Zero WHO}
\label{sec:nzwho}
Our first innovation is `Non-Zero' whitening. When synthesizing detection
templates from rendered images, a common problem is how to handle the
background. If the model is rendered over a natural image background, gradients
in the background will be incorporated into the discriminative template,
potentially causing false-positives if background elements exist in the query
image.

@@

\section{Pose Fine-Tuning via MCMC}
\label{sec:fine}
\input{mcmc}
%
\section{Experiments}
\label{sec:experiments}
\input{experiments}
